An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-08-27 latex_files/images/chapter3/example_post.tex
added Neural net

% This file was created with tikzplotlib v0.9.12.
\begin{tikzpicture}

@@

\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.52,0) rectangle (axis cs:-2.4,0.0231217584119079);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.4,0) rectangle (axis cs:-2.28,0.0357912150759672);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.28,0) rectangle (axis cs:-2.16,0.0432881444129306);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.16,0) rectangle (axis cs:-2.04,0.0678262794417402);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.04,0) rectangle (axis cs:-1.92,0.0853043382950843);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.92,0) rectangle (axis cs:-1.8,0.104057207601703);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.8,0) rectangle (axis cs:-1.68,0.133234851902131);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.68,0) rectangle (axis cs:-1.56,0.165264196422909);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.56,0) rectangle (axis cs:-1.44,0.16070619494247);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.44,0) rectangle (axis cs:-1.32,0.180066797779813);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.32,0) rectangle (axis cs:-1.2,0.221049487169422);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.2,0) rectangle (axis cs:-1.08,0.246171403878041);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.08,0) rectangle (axis cs:-0.96,0.263219759376131);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.96,0) rectangle (axis cs:-0.84,0.275654702395393);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.84,0) rectangle (axis cs:-0.72,0.30275211056918);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.72,0) rectangle (axis cs:-0.6,0.289942517702741);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.6,0) rectangle (axis cs:-0.48,0.327857582723436);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.48,0) rectangle (axis cs:-0.36,0.302668457836128);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.36,0) rectangle (axis cs:-0.24,0.314413087062547);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.24,0) rectangle (axis cs:-0.12,0.319501604166278);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.12,0) rectangle (axis cs:0,0.333969594590972);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0,0) rectangle (axis cs:0.12,0.336688308415186);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.12,0) rectangle (axis cs:0.24,0.311239645561226);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.24,0) rectangle (axis cs:0.36,0.328195053578145);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.36,0) rectangle (axis cs:0.48,0.316839373811389);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.48,0) rectangle (axis cs:0.6,0.315180976253135);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.6,0) rectangle (axis cs:0.72,0.305533027707716);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.72,0) rectangle (axis cs:0.84,0.294804743438855);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.84,0) rectangle (axis cs:0.96,0.270682012152812);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.96,0) rectangle (axis cs:1.08,0.238103562512508);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.08,0) rectangle (axis cs:1.2,0.217233993067405);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.2,0) rectangle (axis cs:1.32,0.213737380323862);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.32,0) rectangle (axis cs:1.44,0.205697780692993);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.44,0) rectangle (axis cs:1.56,0.187837922186227);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.56,0) rectangle (axis cs:1.68,0.140154434384905);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.68,0) rectangle (axis cs:1.8,0.116289453613951);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.8,0) rectangle (axis cs:1.92,0.0886000414831757);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.92,0) rectangle (axis cs:2.04,0.0841267652067261);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.04,0) rectangle (axis cs:2.16,0.0663927432898532);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.16,0) rectangle (axis cs:2.28,0.0377377498258489);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.28,0) rectangle (axis cs:2.4,0.0361079514925686);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.4,0) rectangle (axis cs:2.52,0.0262891225779227);

>>>>

% This file was created by tikzplotlib v0.9.9.
\begin{tikzpicture}

@@

\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.52,0) rectangle (axis cs:-2.4,0.0232073945389685);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.4,0) rectangle (axis cs:-2.28,0.0370673662775194);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.28,0) rectangle (axis cs:-2.16,0.0432283769706026);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.16,0) rectangle (axis cs:-2.04,0.0612233170218504);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-2.04,0) rectangle (axis cs:-1.92,0.0863738703892799);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.92,0) rectangle (axis cs:-1.8,0.109332614272474);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.8,0) rectangle (axis cs:-1.68,0.1270696943844);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.68,0) rectangle (axis cs:-1.56,0.162608319593082);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.56,0) rectangle (axis cs:-1.44,0.165932870953625);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.44,0) rectangle (axis cs:-1.32,0.186184085473939);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.32,0) rectangle (axis cs:-1.2,0.21004533914476);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.2,0) rectangle (axis cs:-1.08,0.260281980894789);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-1.08,0) rectangle (axis cs:-0.96,0.258872960512065);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.96,0) rectangle (axis cs:-0.84,0.267861221254142);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.84,0) rectangle (axis cs:-0.72,0.301309339097609);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.72,0) rectangle (axis cs:-0.6,0.296677069473362);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.6,0) rectangle (axis cs:-0.48,0.318079444437077);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.48,0) rectangle (axis cs:-0.36,0.310739645449952);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.36,0) rectangle (axis cs:-0.24,0.317600561692622);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.24,0) rectangle (axis cs:-0.12,0.313833964721813);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:-0.12,0) rectangle (axis cs:0,0.340218562084569);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0,0) rectangle (axis cs:0.12,0.343469439176735);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.12,0) rectangle (axis cs:0.24,0.315528472894501);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.24,0) rectangle (axis cs:0.36,0.327491332222326);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.36,0) rectangle (axis cs:0.48,0.320667253113843);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.48,0) rectangle (axis cs:0.6,0.309533229305267);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.6,0) rectangle (axis cs:0.72,0.307884767550316);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.72,0) rectangle (axis cs:0.84,0.289208340516575);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.84,0) rectangle (axis cs:0.96,0.272217212371973);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:0.96,0) rectangle (axis cs:1.08,0.235895798061777);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.08,0) rectangle (axis cs:1.2,0.221437222892658);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.2,0) rectangle (axis cs:1.32,0.207761436825051);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.32,0) rectangle (axis cs:1.44,0.206149812204291);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.44,0) rectangle (axis cs:1.56,0.191175517156526);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.56,0) rectangle (axis cs:1.68,0.130919174907133);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.68,0) rectangle (axis cs:1.8,0.118127480060059);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.8,0) rectangle (axis cs:1.92,0.0924796253810799);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:1.92,0) rectangle (axis cs:2.04,0.0812258808863897);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.04,0) rectangle (axis cs:2.16,0.0618587575866078);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.16,0) rectangle (axis cs:2.28,0.0384119216754122);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.28,0) rectangle (axis cs:2.4,0.0377120161258239);
\draw[draw=none,fill=color0,fill opacity=0.5] (axis cs:2.4,0) rectangle (axis cs:2.52,0.026430643780492);
